---
title: "Woolworth Store Sales Model"
author: "Ashish Singh"
date: "February 25, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo = FALSE, message=FALSE}
library(ggplot2)
library(reshape2)
library(knitr)
library(formattable)
library(dplyr)
library(xts)

#woolworth_sales <- read.csv("https://raw.githubusercontent.com/winappsdave/winapps_challenge/master/stores.csv", header = TRUE, sep=",", check.names = FALSE)
woolworth_sales <- read.csv("/media/thethakuri/Share/stores.csv")
woolworth_sales$Date <- as.Date(woolworth_sales$Date, format= "%d/%m/%Y")
```
# Woolworth Weekly Sales Model
## $$\widehat{Y} = 39243.231 + 89263.9H + 1.382S - 1785.266T - 6533.111U - 616.662C + 75.078P  - 38.735P_{65} + 58.399P_{18}$$
    where   
      
    Y = expected weekly sales of the store
    H = 1 if Holiday else 0
    S = the size of the store
    T = average temperature in the region
    U = the unemployment rate
    C = the unemployment rate
    P = population in the region
    P_65 = population over 65 in the region
    P_18 = population under 18 in the region
    
    We have, 
    Adjusted R-squared = 0.8806

# Time Series Analysis
```{r echo=FALSE}
plot_ts <- function(store_no){
  store_ts <- subset(woolworth_sales, Store==store_no, select = c(Date, Weekly_Sales))
  store_ts$Weekly_Sales <- xts(store_ts$Weekly_Sales, order.by = store_ts$Date)
  return(plot(apply.monthly(store_ts$Weekly_Sales, mean), ylim = range(store_ts$Weekly_Sales), main = "", ylab = "Weekly Sales in Thousands"))
}
```

## Time Series Analysis for Store 1
```{r echo=FALSE}
plot_ts(1)
```

## Time Series Analysis for Store 13
```{r echo=FALSE}
plot_ts(13)
```

## Time Series Analysis for Store 27
```{r echo=FALSE}
plot_ts(27)
```


# Sales Data Summary
```{r echo=FALSE}
#Omitting Date & Store No.
woolworth_sales <- select(woolworth_sales, -Date, -Store)
summary(woolworth_sales)
```
# Linear multiple regression model
```{r echo=FALSE}
sales_lm <- lm(Weekly_Sales ~ ., data = woolworth_sales)
summary(sales_lm)
```
As Fuel Price and Average earnings are of low significance, we will drop them from our model
```{r}
sales_lm <- lm(Weekly_Sales ~ ., data = select(woolworth_sales, -Fuel_Price, -Average_earning))
summary(sales_lm)
```
As we can see, there is no change in our R-squared of 0.8808

# Plotting model fit

You can also embed plots, for example:

```{r, echo=FALSE}
plot(sales_lm)
```
# Our coefficients
```{r}
round(sales_lm$coefficients, digits = 3)

```
